The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-01-17 SC-challenge.tex
Merging

Multiple groups, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize citation practices; some of the observations and recommendations made here come from these groups.
Our efforts follow similar work by DataCite and the FORCE11 Data Citation Synthesis Group~\cite{DataCitation2014} to standardize research data citation practices.
Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).

@@

Key challenges and research directions include the need to:
\begin{itemize}
\item identify necessary metadata associated with software for citation, 
\item standardize proper formats for citing software in publications,
\item establish mechanisms for software to cite other software (i.e., dependencies),
% I feel like we should point out that this problem has been solved by multiple communities already (Node.js/NPM, Ruby/Gemfile)
\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,
\item determine standard practices for peer review of software, and
\item increase cultural acceptance of the concept of software as a digital product.
\end{itemize}

>>>>

Multiple groups, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize citation practices; some of the observations and recommendations made here come from these groups.
Our efforts follow similar work by DataCite and the FORCE11 Data Citation Synthesis Group~\cite{DataCitation2014} to standardize research data citation practices.
Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).

@@

Key challenges and research directions include the need to:
\begin{itemize}
\item identify necessary metadata associated with software for citation,
\item standardize proper formats for citing software in publications,
\item establish mechanisms for software to cite other software (i.e., dependencies),
% I feel like we should point out that this problem has been solved by multiple communities already (Node.js/NPM, Ruby/Gemfile)
% Also, perhaps we should cite existing efforts around automating this including https://libraries.io & http://depsy.org?
\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,
\item determine standard practices for peer review of software, and
\item increase cultural acceptance of the concept of software as a digital product.
\end{itemize}
